Visit Scotland Notebook

### 2023-06-12 visit_scotland_notebook.Rmd
Started Domestic vs. International Analysis

```{r}
library(tidyverse)
library(here)
```

@@

```{r}
domestic_2017_2019 <- regional_domestic_tourism %>% 
  filter(date_code == "2017-2019",
         region_of_residence == "All of GB") %>% 
  select(expenditure)

international_2017_2019 <- international_visits %>%
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2017, 2018, 2019)) %>% 
  summarise(total_visits = sum(visits),
            total_spend = sum(spend),
            exp_per_visit = total_spend / total_visits) %>% 
  select(total_spend)

tibble(a = c("Domestic", "International"),
       b = c(domestic_2017_2019$expenditure, international_2017_2019$total_spend)) %>% 
  ggplot() +
  geom_col(aes(x = a, y = b)) +
  labs(
    x = "",
    y = "Expenditure \n",
    title = "Domestic vs. International Expenditure",
    subtitle = "2017-2019")
```
### International

@@

>>>>

```{r}
library(tidyverse)
library(here)
library(modelr)
```

@@

```{r}
domestic_2017_2019_spend <- regional_domestic_tourism %>% 
  filter(date_code == "2017-2019",
         region_of_residence == "All of GB") %>% 
  select(expenditure)

international_2017_2019_spend <- international_visits %>%
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2017, 2018, 2019)) %>% 
  summarise(total_visits = sum(visits),
            total_spend = sum(spend),
            exp_per_visit = total_spend / total_visits) %>% 
  select(total_spend)

tibble(a = c("Domestic", "International"),
       b = c(domestic_2017_2019_spend$expenditure, international_2017_2019_spend$total_spend)) %>% 
  ggplot() +
  geom_col(aes(x = a, y = b)) +
  labs(
    x = "",
    y = "Expenditure \n",
    title = "Domestic vs. International Expenditure",
    subtitle = "2017-2019")
```

```{r}
ips_2002_2019 %>%
  add_predictions(model) %>%
  add_residuals(model) %>% 
  ggplot(aes(x = visits, y = spend)) +
  geom_point() +
  geom_line(aes(y = pred), col = "red") +
  annotate("text", x = 1675, y = 2500, label = "spend ~ visits") +
  annotate("text", x = 1930, y = 2300, label = "b1 = 0.81800 / p-value = 4.78e-06") +
  annotate("text", x = 2170, y = 2100, label = "R-Squared = 0.8876 / Residual Standard Error: 183.3") +
  annotate("text", x = 1800, y = 1900, label = "Standard Error: 0.08115")
```

Diagnostic Plots: Ok, not great but passable.

- R-squared: The proportion of variance explained by the predictor(s).

- p-value: Statistical significance of effect.

- Residual Standard Error: Average distance that the observed values fall from the regression line. The smaller the value, the better the regression model is able to fit the data.

- Standard error: Uncertainty around estimated coefficient.

### International

@@

### USA
